Multiproxy analysis exploring patterns of diet and disease in dental calculus and skeletal remains from a 19th century Dutch population

### 2023-11-03 analysis/paper/paper.tex
tweak figure

\newgeometry{top=30mm,left=30mm}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

>>>>

\newgeometry{top=30mm,left=30mm}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden]}{\end{tcolorbox}}\fi
